Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-23 ms.tex
more notes to self, other minor tweaks

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible in \PLANCK~857 GHz, but can 
be perceived at a low level in \PLANCK~545 GHz, and are prominent in 
\PLANCK~217 GHz and 353 GHz relative to the Galactic emission we wish to 
characterize, especially at high latitudes. To remove the CMB anisotropies, we 
have subtracted the Spectral Matching Independent Component Analysis 
(\verb|SMICA|) model from each of the \PLANCK~maps \citep{smica}, after 
applying appropriate unit conversions. Removal of the residual Solar dipole at 
low frequencies is discussed in $\S$\ref{sec:zp}.
% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz

@@

The offset and residual dipole parameters for \PLANCK~217 GHz were not 
available from \cite{planckdust} Table 1. In order to set the zero-point of 
Galactic emission in the 217 GHz map, we simultaneously fit the constant 
offset and residual dipole amplitude. Restricting to regions of low column 
density (H\,\textsc{i} $<$ 200 K km/s for $-72$$<$$v_{LSR}$$<$$+25$ km/s), we 
modeled the 217 GHz map as:

@@

\subsection{Finite Bandpass Correction}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
 of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
nominal band center frequencies for which we have measurements, $\nu_i \in$
\{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum $M_{\nu}$ is only
dependent upon one parameter: the hot dust temperature $T_2$. We have used the 
\PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
used the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note 
that it is not clear which bandpass should properly be ascribed to the 
\IRAS/DIRBE composite 100$\mu$m maps under consideration. 
% (here SFD \verb|i100|) and that of \cite{planckdust}).

@@

@@

@@

>>>>

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible in \PLANCK~857 GHz, but can 
be perceived at a low level in \PLANCK~545 GHz, and are prominent in 
\PLANCK~217 GHz and 353 GHz relative to the Galactic emission we wish to 
characterize, especially at high latitudes. To remove the CMB anisotropies, we 
have subtracted the Spectral Matching Independent Component Analysis 
(\verb|SMICA|) model from each of the \PLANCK~maps \citep{smica}, after 
applying appropriate unit conversions. Removal of the residual Solar dipole at 
low frequencies is discussed in $\S$\ref{sec:zp}.
% SMICA is subtracted from ALL Planck maps being used, including 545, 857 GHz
% WHAT IS THE ANGULAR RESOLUTION OF THE SMICA MAP, AND IS IT EVEN
% WELL-DEFINED??

@@

The offset and residual dipole parameters for \PLANCK~217 GHz were not 
available from \cite{planckdust} Table 1. In order to set the zero-point of 
Galactic emission in the 217 GHz map, we simultaneously fit the constant 
offset and residual dipole amplitude. Restricting to regions of low column 
density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
km\,s$^{-1}$), we modeled the 217 GHz map as:

@@

\subsection{Finite Bandpass Correction}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
 of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
nominal band center frequencies for which we have broadband measurements, 
$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum 
$M_{\nu}$ is only dependent upon one parameter: the hot dust temperature $T_2$.
 We have used the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note that 
it is not clear which bandpass should properly be ascribed to the \IRAS/DIRBE 
composite 100$\mu$m maps under consideration. 
% (here SFD \verb|i100|) and that of \cite{planckdust}).

@@

% check whether I545 normalization parameter is the monochromatic
% 545 GHz intensity, or if it is for the Planck bandpass
% i think it should eventually be monochromatic, since that will be
% more useful to people who want SED predictions

@@

% is I_nu on RHS inclusive of offsets or is it the ``pure'' thermal dust
% intensity

@@

%at some point in this should make statements re: the fact that in terms
%of predicting *emission* the conversion to tau is unnecessary and
%and actually the raw uncertainty on Ghz 545 amplitude is the relevant quantity
